Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-28 surfaces-write-up/surface-write-up.tex
removing sentient computations...

Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
Then a careful computation deduces that we can write

>>>>

Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
By a careful computation, we can write
